Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Remove a comment
Make abstract more focused

\begin{abstract}

When wading through the numerous libraries written by
the Haskell community, one sometimes gets the impression that the type
system is being too much relied on, at the expense of testing.
While the type system cannot always guarantee semantic correctness,
test code has more applications than getting the code correct.
Test code assists developers in maintaining correctness when extending
software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools:
Doctest integrated with QuickCheck for user documentation and
Hspec with new mnemonic combinators for code documentation.
Our approach can be used for design, documentation and automated
testing.  We hope that this motivates Haskell programmers to write
more and better tests.

@@

\begin{quote}
    TBD

    sol: I think it is not critical.  I'll try to resolve this
    tomorrow, but I think we can always remove it.

\begin{itemize}

\item It is important that testing is automated, including running of test
    suites.  Where should we put this?

\item automatically sounds strange, better use automated somehow
\end{itemize}
\end{quote}

>>>>

\begin{abstract}
We observed that several widely used Haskell libraries do not have
tests.
Test code assists developers in maintaining correctness when extending
software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools:
Doctest integrated with QuickCheck for user documentation and
Hspec with new mnemonic combinators for code documentation.
Our approach can be used for design, documentation and automated
testing.  We hope that this motivates Haskell programmers to write
more and better tests.

@@
